Machine Learning for Predictive Auto-Tuning with Boosted Regression Trees

### 2012-03-01 paper/final.tex
Starting to work on the final version

\author{
%\alignauthor First Last\titlenote{}\\
\alignauthor First Last\\
\affaddr{Affiliation line 1}\\
\affaddr{Affiliation line 2}\\
\email{anon@mail.com}
% 2nd author
%\alignauthor First Last\titlenote{None}\\
\alignauthor First Last\\
\affaddr{Affiliation line 1}\\
\affaddr{Affiliation line 2}\\
\email{anon@mail.com}
% 3rd author
%\alignauthor First Last\titlenote{None}\\
\alignauthor First Last\\
\affaddr{Affiliation line 1}\\
\affaddr{Affiliation line 2}\\
\email{anon@mail.com}
}

@@

For the implementation features $b$, we directly used the integer and binary
% XXX: MANUAL HYPHENATION
values (block\_w, block\_h, etc.) that paramet-rized the kernels.  We did not
use platform features ($c$) in our experiments. We leave the investigation of
cross-platform predictive auto-tuning for future work.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{illustrator/fig_allstars_mixup_580_R1.pdf}
\caption{Different arguments call for different kernels:
{\em left} is the average argument-specific empirical
auto-tuned performance across 100 random argument configurations,
{\em middle} is the average speed of our reference implementation,
{\em right} is the average speed of kernels auto-tuned for different argument
configurations than the one being tested.  For 38 out of 100 random configurations, the
kernel auto-tuned for another problem could not even run on the GTX 295
hardware.  These points contributed a speed of 0, bringing down the average
much lower than the reference.  Good performance across a variety of inputs
requires {\em input-dependent auto-tuning}.
}
\label{fig:allstars}
\end{figure}

>>>>

\author{
\alignauthor James Bergstra\\
\affaddr{\small{Rowland Institute at Harvard}}\\
\affaddr{\small{Cambridge MA, US}}\\
\email{\emph{\small{bergstra@rowland.harvard.edu}}}
% 2nd author
\alignauthor Nicolas Pinto\\
\affaddr{\small{Rowland Institute at Harvard}}\\
\affaddr{\small{McGovern Institute at MIT}}\\
\affaddr{\small{Cambridge MA, USA}}\\
\email{\emph{\small{pinto@rowland.harvard.edu}}}
% 3rd author
\alignauthor David Cox\\
\affaddr{\small{Rowland Institute at Harvard}}\\
\affaddr{\small{Cambridge MA, USA}}\\
\email{\emph{\small{cox@harvard.rowland.edu}}}
}

@@

For the implementation features $b$, we directly used the integer and binary
values (block\_w, block\_h, etc.) that paramet-rized the kernels.  We did not
use platform features ($c$) in our experiments. We leave the investigation of
cross-platform predictive auto-tuning for future work.

@@

\begin{figure}[!t]
\centering
\includegraphics[width=\linewidth]{illustrator/fig_allstars_mixup_580_R2.pdf}
\caption{Different arguments call for different kernels:
{\em left} is the average argument-specific empirical
auto-tuned performance across 100 random argument configurations,
{\em middle} is the average speed of our reference implementation,
{\em right} is the average speed of kernels auto-tuned for different argument
configurations than the one being tested.  For 38 out of 100 random configurations, the
kernel auto-tuned for another problem could not even run on the GTX 295
hardware.  These points contributed a speed of 0, bringing down the average
much lower than the reference.  Good performance across a variety of inputs
requires {\em input-dependent auto-tuning}.
}
\label{fig:allstars}
\end{figure}
